---
title: "A Measure Validation of the PECTAC Instrument"
author: "Billy Jackson"
date: "July 6, 2017"
output:
  rmdformats::readthedown:
    highlight: tango
    code_folding: "hide"
---

Two things left to do:  

1.  Create table of highest and least "top 2" rankings
2.  Fix table at end of How Parents are Paying for College

```{r Set knitr options, echo = FALSE, cache = FALSE}
# Set chunks options
knitr::opts_chunk$set(message = FALSE, 
                      cache = TRUE, 
                      prompt = FALSE, 
                      tidy = TRUE, 
                      comment = NA, 
                      warning = FALSE)
knitr::opts_knit$set(width=75)
```

```{r Libraries, message = FALSE, warning = FALSE, echo = FALSE, cache=FALSE}
# Load libraries for factor analysis, exporting tables, cron's alpha, and tidyverse
library(psy); library(tidyverse); library(lavaan); library(psych); library(knitr); library(DT); library(Hmisc)
# library(caret)
```

# Overview

This is a notebook used by Billy Jackson to perform statistical analyses for the paper:  
*A Measure Validation of the PECTAC Instrument*  

My game plan in this report is to:  

* Become familiar with the previously collected PECTAC data 
* Perform descriptive analyses
* Assess the validity of the instrument by means of a CFA and analysis of Cronbach's alpha coefficient
* Identify which items parents found most and least important
* Analyze how parents are paying for college
* Determine if there are any relationships between income, method of payment, and expectations  


The code has been set to hidden for ease of readability.  That option can be changed universally at the top, but I would recommend viewing the code in chunks as desired.

*****


# Exploring the Data

## Loading and exploring the data

```{r Load dataset}
# Read in raw dataset
PECTAC <- read_csv("MeasureValidationStudyPECTAC2014.csv")

# Getting familiar with variables and dataset
datatable(PECTAC, caption = "Table 1: PECTAC Results", fillContainer = FALSE)
```

The raw data (Table 1 above) contains 821 observations of 167 variables.  Variables 1-14 are responses to demographic questions.  Questions 15 through 150 are related to the scales of the PECTAC instrument.  In each scale, the first half of the variables in each scale are the responses to the items themselves and the second half are the results to the "rate top two" question at the end of each scale.  More specifically:

Scale         |  Likert-Scale Questions | Rank           |
:-----------: | :---------------------: | :------------: |
Tech          | 15-29                   | 30-44
ATL           | 45-54                   | 55-64
OCL           | 65-77                   | 78-90
CF            | 91-99                   | 100-108
CUC           | 109-118                 | 119-128
BPP           | 129-139                 | 140-150

Where:

* Tech = Tech Resources in Support of Student Learning
* ATL = Active & Team Learning
* OCL = Out of Class Learning Opportunities
* CF = A Caring Faculty
* CUC = A Caring University Community
* BPP = Being in Partnership with Parents

Questions 151 & 152 are about receiving grants (yes/no, amount).  
Questions 153-166 is COFHE data.  Are parents planning to pay for their child's college by:

* Use of family assets (153-157)
* Parental borrowing (158-163)
* Current parent income (164-166)  

How much annual income the family earns is column 167.

## Transforming COFHE data

```{r Viewing Paying for College Data, collapse = TRUE}
# Paying for college subset of data
(select(PECTAC, 153:166))  
  
```

The COFHE financial data (see snippet inside code above) asked parents to respond whether partitions of their payment for their child's college was in the range of 0%, 1-25%, 26-50%, or 51-100%.  This introduced a lot of issues where parents' proportions came out to be well over 100% or under 100% in total.  To deal with this error, I will use a re-scaling method used by COFHE researcher Steve Micicucci.  The method imputes point estimates for each possible response as shown in the table below:

Response      |Range          | Point Estimate
:-----------: | :-----------: | :------------:
1             |0%             | 0
2             |1% - 25%       | .125
3             |26% - 50%      | .375
4             |51% - 100%     | .67

The method then calculates the sum of the imputed point estimate shares and divides each payment share by its sum to achieve a true proportional share.  Note: COFHE researchers deemed sums of payment less than 0.38 too unreliable to scale and extract meaningful results from, so I will follow their recommendation and set those financial records to NA.

```{r COFHE inside dataset 1}
# Replace responses with point estimates
PECTAC[, 153:166][is.na(PECTAC[, 153:166])] <- 0
PECTAC[, 153:166][PECTAC[, 153:166] == 1] <- 0
PECTAC[, 153:166][PECTAC[, 153:166] == 2] <- 0.125
PECTAC[, 153:166][PECTAC[, 153:166] == 3] <- 0.375
PECTAC[, 153:166][PECTAC[, 153:166] == 4] <- 0.67

# View a snapshot of the results
(PECTAC %>% 
        select(153:166))
```

```{r COFHE 2, results='hold'}
# Calculating sum of imputed shares
PECTAC <- PECTAC %>% 
        mutate(totals = rowSums(PECTAC[,153:166]))

# Set very incomplete cases (sum < 0.38) to NA
PECTAC$totals[PECTAC$totals < 0.38] <- NA

# Scale up/down values
PECTAC[,153:166] <- PECTAC[153:166]/PECTAC$totals
# this will set finan. values across the board to NA for incomplete cases

# Check that sum of props = 1 or NA
PECTAC$totals <- rowSums(PECTAC[,153:166])

# View the results
datatable(PECTAC[,153:168])
```

Looking at the totals column, I noticed that the last 100 entries were all NA for the COFHE data.  Upon looking further into that, it turns out that many of the later respondents didn't answer many of the questions, especially the financial data questions.  Something to talk to Justin about.

*****

# Descriptive Analysis

## Demographics
```{r Demographics, collapse=TRUE}
# Proportion of parent respondents by gender (1) = Female, (2) = Male
table(PECTAC$ParentGen)/821


# Proportion of parents marital status
table(PECTAC$MaritalStat)/821


# Proportion of students gender responded on behalf of
table(PECTAC$StudentGen)/821


# Proportion of parents race/ethnicity
table(PECTAC$RaceEthnic)/821


# Proportion of English First Language
table(PECTAC$EngYesNo)/821


# Proportion of parents Educational Level
table(PECTAC$EdLevel)/821
  
  
# Proportion of First Experience as College Parent
table(PECTAC$FirstPCExp)/821
  
  
# Summary of number of childeren
table(PECTAC$NumChild)/821


mean(PECTAC$NumChild, na.rm = TRUE)


sd(PECTAC$NumChild, na.rm = TRUE)
  
  
# Summary of parent involvement in college choice
table(PECTAC[,10])/length(PECTAC[,10])


```

There were 821 parent respondents of the survey.  The respondents were mostly female (76.2%) and responding on behalf of mostly female students (65.0%).  74.5% of respondents were married.  Respondents largely identified as Caucasian (79.9%) and 95.5% reported speaking English as a first language.  Slightly over half (52.4%) of respondents had graduated college with a bachelor degree or higher and 98.2% of respondents had at minimum a high school degree.  Respondents had an average of 2.3 children with a standard deviation of 1.0.  For 62.4% of parents responding, this was their first child in college.


## Descriptive statistics

Going to take a look at the descriptive stats for each variable.  Of interest will be the mean, sd, skew, and kurtosis.

```{r Subsetting by section and sub-section}
# Subsetting by section and sub-section
demographic <- select(PECTAC, 1:14)

# Teaching sections
Tech <- select(PECTAC, 15:29)
ATL <- select(PECTAC, 45:54)
OCL <- select(PECTAC, 65:77)
teaching <- cbind(Tech, ATL, OCL)

# Caring sections
CF <- select(PECTAC, 91:99)
CUC <- select(PECTAC, 109:118)
BPP <- select(PECTAC, 129:139)
caring <- cbind(CF, CUC, BPP)

# Financial sections
financials <- select(PECTAC, 151:167)
TaxIncome2013 <- select(PECTAC, FamilyIncome2013BTax)
```

```{r Descriptive Stats for each variable, results = 'hold'}
# Function to get the descriptive stats of interest for a dataset
var_descriptive_stats <- function(dataset) {  
    dataset %>%  
        psych::describe() %>%  
        round(digits = 2) %>%  
        select(n, mean, sd, skew, kurtosis)  
}

# Print out table of descriptive stats for all of the variables
datatable(var_descriptive_stats(teaching), caption = "PECTAC Teaching")  
datatable(var_descriptive_stats(caring), caption = "PECTAC Caring")
```

Within the teaching section, every item (n = 531) was found to have a mean between 1 and 3 with a positive skew indicating that parents showed a general feeling of Very Important or Important towards those items. In the caring section, every item (n = 582) was also found to have a mean score between 1 and 3 with a positive skew. Hence, parent respondents showed a general feeling of Very Important or Important towards those items as well.

Next to look at is the descriptive statistics of each section (teaching, caring) and each of the six sub-sections.  Of interest will be the mean, sd, skew, and kurtosis.

```{r Scale Descriptive Statistics, results='asis'}
# Function to get the descriptive stats for an entire scale by unlisting the variables
scale_descriptive_stats <- function(dataset) {
    dataset %>% 
        unlist(use.names = FALSE) %>% 
        psych::describe() %>% 
        round(digit = 2) %>% 
        select(n, mean, sd, skew, kurtosis)
}

# Get the descriptive stats
Tech_stats <- scale_descriptive_stats(Tech)
ATL_stats <- scale_descriptive_stats(ATL)
OCL_stats <- scale_descriptive_stats(OCL)
CF_stats <- scale_descriptive_stats(CF)
CUC_stats <- scale_descriptive_stats(CUC)
BPP_stats <- scale_descriptive_stats(BPP)

# Combine into one single table
scale_stats <- rbind(Tech_stats, ATL_stats, OCL_stats, CF_stats, CUC_stats, BPP_stats)
row.names(scale_stats) <- c("Tech", "ATL", "OCL", "CF", "CUC", "BPP")
datatable(scale_stats, caption = "PECTAC Scales")
```

The scale statistics are similar to the individual variable statistics -- each carrying a mean between 1 and 2 with a positive skew indicating that parents generally feel that all of the scales carry some importance.

*****

# Instrument Validity

The game plan:

* Compute KMO index to determine suitability for factor analysis
* Perform a Confirmatory Factor Analysis (CFA) with the `lavaan` package (version 0.5-23.1097)
    + Check for RMSEA < 0.06
    + Check for SRMR (Standardized Root Mean Residual) < 0.08
    + Check for CFI (Comparative Fit Index) > 0.95

## KMO Index

If the KMO index is high (nearly 1), the factor analysis can act efficiently.  If KMO is low (near 0), the factor analysis will not be relevant (Kaiser, 1974).  There is a `KMO` function in the `psych` package to perform this.

```{r KMO, results = 'hold'}
# Kaiser-Meyer-Olkin measure of sampling adequacy
teaching_cor_matrix <- cor(teaching, use = "complete.obs")
caring_cor_matrix <- cor(caring, use = "complete.obs")
KMO(teaching_cor_matrix)
KMO(caring_cor_matrix)
```

The teaching section obtained a measure of sampling adequacy (MSA) of 0.90. The caring section obtained a MSA of 0.91. Based on Kaiser’s valuations of KMO test results, the MSA scores of PECTAC sub-section indicates the sampling is more than adequate for factor analysis (Kaiser, 1974).


## Confirmatory Factor Analysis

I'll fit the CFA using a diagonally weighted least squares with mean and variance adjustment (DWLSMV) estimator.
DWLSMV estimator is a preferred choice for non-normal data, and specifically, ordinal data such as likert-scale data. (Li, 2016)

```{r Confirmatory Factor Analysis - Teaching, message=FALSE, warning=FALSE}
# Define lavaan teaching model
teaching_model <- "Tech =~ TechAAvWeb + TechWebAccessRDA + TechWebAccessTF + TechWebAccessFA + TechSAAWeb + TechEmail + TechBooks + TechCLabs + TechInternetResHall + TechWireless + TechLibrary + TechUnivLaptop +
TechFacultyEmail + TechAcademicContentWeb + TechAAEmail
                ATL =~ ATLDiscuss + ATLPresent + ATLOutperform + ATLGroupProject +  ATLOnline + ATLCommunityService + ATLInternetResearch + ATLWebAssign + ATLMoreIT + ATLFeedback 
                OCL =~ OCLResponsible + OCLClubs + OCLAdditionalAA + OCLInternships + OCLRaceCulture + OCLServeVolunteer + OCLArea + OCLRemedialDisibility + OCLAccessTutorASupport + OCLSocialGroup + OCLPracticumIntern + OCLCareerCounsel + OCLMorals"

# Fit a CFA model and display summary output
CFA_teaching <- cfa(teaching_model, data = teaching, estimator = "WLSMV")
summary(CFA_teaching, fit.measures = TRUE)
```


For the Teaching section (n = 531), latent variables of Tech, ATL, and OCL were defined by the indicator variables in each respective scale. The CFA showed a diagonally weighted least squares test statistic of 1376.2 (p < 0.001). The RMSEA = 0.045 is below 0.06, therefore is low enough to be indicative of acceptable model fit. The SRMR = 0.074 falls below the maximum 0.08 cut-off criteria for an acceptable model. The Comparative Fit Index (CFI) 0.957, which is greater than the minimum threshold of 0.95 to be considered an indicator of good fit (Hooper, Coughlan, & Mullen, 2008). Based on the results of those CFA elements, the factor structure was determined as adequate for the PECTAC teaching section.


```{r Confirmatory Factor Analysis - Caring, message=FALSE, warning=FALSE}
# Define lavaan caring model
caring_model <- "CF =~ CFContactAA + CFMajorAA + CFKnownByF + CFKnownByInstructor + CFFairTreatment + CFAccessOutOfClass + CFGiveFeedback + CFAdditionalTutoring + CFFOrTA
                CUC =~ CUCWProgram + CUCLeadership + CUCUnique + CUCOrientation +  CUCParentSupChallenge + CUCHealth + CUCComOthers + CUCRAFriend + CUCFaith + CUCCounseling 
                BPP =~ BPPNotifyASuccess + BPPCheat + BPP24CallRet + BPPSecure + BPPMDProgress + BPPDicipline + BPPAATutorMentor + BPPIllegalSub + BPPOrientInvolve + BPPCounseling + BPPIllegalDrink"

# Fit a CFA model and display summary output
CFA_caring <- cfa(caring_model, data = caring, estimator = "WLSMV")
summary(CFA_caring, fit.measures=TRUE)
```

For the Caring section (n = 582), latent variables of CF, CUC, and BPP were also defined by the indicator variables in each respective scale. The CFA showed a DWLS test statistic of 700.9 (p < 0.001). The RMSEA = 0.036 and SRMR = 0.069 both fell below the cut-off criteria of RMSEA < 0.06 and SRMR < 0.08 for acceptable models. A CFI calculated at 0.981 was above the 0.95 cut-off which also indicates a good fit. Based on those results, the factor structure was determined as adequate for the PECTAC caring section.


*****

## Internal reliability (Cronbach's alpha)
```{r Cronbachs alpha, collapse = TRUE}
# Compute Cronbachs alpha for each scale
cronbach_stats <- function(dataset) {
    dataset %>% 
        cronbach() %>% 
        unlist() %>% 
        round(digits = 3)
}

# Create table of alpha coefficients
alpha_table <- data.frame(rbind(cronbach_stats(Tech), cronbach_stats(ATL), cronbach_stats(OCL), cronbach_stats(CF), cronbach_stats(CUC), cronbach_stats(BPP)))

row.names(alpha_table) <- c("Tech", "ATL", "OCL", "CF", "CUC", "BPP")

kable(alpha_table, align = 'c')
```

Each of the six PECTAC expectation scales was shown to be independently sufficiently reliable, with each scale’s Cronbach’s alpha coefficient between 0.70 and 1.00 (Nunnally, 1978). This is interpreted as evidence that each scale of items reliably measures the same underlying idea.  

Based on the CFA and internal consistency Cronbach’s alpha scores, the researchers find the PECTAC expectations scales to be sufficiently reliable.

*****
    
# Most and Least Important Items

Each of the PECTAC scales contained a final question asking respondents:

> *Out of these items, which two are the most important to you as a parent? (select two)* 

These responses hope to be instrumental in gauging what parents find most and least important.  It was observed that several respondents selected more or less than two choices in their "top two".  An example of the Tech scale is shown below.
```{r Viewing top two, collapse=TRUE}
# Scales with two two most important data included
# Checking the sums
(PECTAC %>% 
    select(30:44) %>% 
    rowSums(na.rm = TRUE) %>% 
    table())
```
For analysis, I will only consider valid responses those who ranked 0, 1, or 2 items.



```{r Getting scales with top two}
# Function to get valid top-two rankings
validtoptwo <- function(dataset, cols) {
    Temp <- dataset[,cols]
    Temp$sum <- rowSums(Temp, na.rm = TRUE)
    valid <- filter(Temp, sum <= 2)
}

# Storing the valid responses
RankTech <- validtoptwo(PECTAC, 30:44)
RankATL <- validtoptwo(PECTAC, 55:64)
RankOCL <- validtoptwo(PECTAC, 78:90)
RankCF <- validtoptwo(PECTAC, 100:108)
RankCUC <- validtoptwo(PECTAC, 119:128)
RankBPP <- validtoptwo(PECTAC, 140:150)

```


```{r Frequencies for each item in each scale, results='asis', collapse=TRUE}
Techsums <- colSums(RankTech, na.rm = TRUE)
ATLsums <- colSums(RankATL, na.rm = TRUE)
OCLsums <- colSums(RankOCL, na.rm = TRUE)
CFsums <- colSums(RankCF, na.rm = TRUE)
CUCsums <- colSums(RankCUC, na.rm = TRUE)
BPPsums <- colSums(RankBPP, na.rm = TRUE)
```


Each expectation item received at least one selection as the most important. Items selected as most important by 250 parents and those selected by 25 or less parents are displayed in Tables 4 and 5 respectively.

*****

# How Parents are Paying for College

Some things to analyze in this section:

* How are parents paying for college?
* Does how they pay for college affect their expectations?
* Does their income level affect their expectations?

```{r Singular Values for Fam Assets, PBorrow, and CPI}
# Get singular values for each respondent for the 3 different types of payment method
FamAssets <- rowSums(PECTAC[,153:157])
PBorrow <- rowSums(PECTAC[,158:163])
CPI <- rowSums(PECTAC[,164:166])
```


```{r Creating Finances Data Frame}
# Create finances data frame
finances <- as.data.frame(cbind(PECTAC$FamilyIncome2013BTax, FamAssets, PBorrow, CPI, PECTAC$GrantAidYesNo, PECTAC$GrantAidAMT))

names(finances)[c(1,5,6)] <- c("FamilyIncome", "GrantAidYesNo", "GrantAidAMT")
```

```{r Grant Aid, collapse=TRUE}
# Grant Aid Yes(1) or No(2)
table(finances$GrantAidYesNo)  
  
prop.table(table(finances$GrantAidYesNo))


# Grant Aid AMT (1) = $1 - $4,999, (2) = $5,000 - $9,999, (3) = $10,000 - $14,999, (4) = $15,000 - $19,999, (5) = $20,000 - $24,999, (6) = $25,000 - $29,999, (7) = $30,000-$39,999, (8) = $40,000 or more
table(finances$GrantAidAMT)  
  
# Filter out incomplete cases and those with grant aid > 8
complete.finances <- filter(finances, complete.cases(finances), GrantAidAMT <= 8)
table(complete.finances$GrantAidAMT)
  
sum(table(complete.finances$GrantAidAMT))  
  
prop.table(table(complete.finances$GrantAidAMT))
```

```{r Finance proportions overvew}
# What proportions were parents paying by fin assets, par borrowing, and cpi
kable(prop.table(colSums(finances[,2:4], na.rm = TRUE)), caption = "Proportions of payment method")
```

567 respondents reported to be using grant aid in paying for college.  510 of those respondents reported a valid grant aid amount as values of (9) and (10) were invalid responses.  For college costs not covered by grant aid, there appears to be even distribution of what methods parents used to pay for their child’s college. 35.6% of parental contributions to college payment comes from use of family assets, 31.7% comes from parental borrowing, and 32.7% comes from current parent income.  

As one of the goals of the study is to determine pre-college payment mechanics in order to potentially inform financial education and literacy, I'm interested in AMT data of these parents. 

*** THIS NEEDS TO BE FIXED BELOW ***
```{r  Proportions by pre-college/actual college}
# Creating pre-college/actual college subsets
question10 <- as.data.frame(cbind(FamAssets, PBorrow, CPI, PECTAC$YearInSchool))
names(question10)[4] <- "YearInSchool"
complete.question10 <- filter(question10, complete.cases(question10) == TRUE)

precollege <- complete.question10[complete.question10$YearInSchool == 1,]
college <- complete.question10[complete.question10$YearInSchool > 1,]

# Table of proportions
precollege.props <- prop.table(colSums(precollege[,1:3], na.rm = TRUE))
college.props <- prop.table(colSums(college[,1:3], na.rm = TRUE))
pre_post_payment_table <- rbind(precollege.props*40, college.props*495)
kable(pre_post_payment_table)
```


The proportions by pre-college and in/post-college are shown in Table 7 above. A chi-square test shows there to be no significant difference between the two sets of proportions though.

*****

# Relationships among Finances and Expectations

## Relationship between income and method of payment

The researchers noticed some significant relationships by analyzing a correlation matrix of parents’ income and payment methods. Generally, parents with the higher tax income were using more family assets to pay for their child’s college. Family assets were described as; ordinary savings and sale of stock or other financial assets, sale of non-financial assets (real estate, etc.), state-sponsored college savings (“529”) plan, pre-paid tuition plan, or a withdrawal from a retirement account. Conversely, parents with lower tax income reported borrowing money to pay for college, mostly from federal or private loans. The correlation matrix of income and payment methods is listed in the table below.
```{r Finances cor matrix, results = 'asis'}
# Correlation matrix of tax income with method of payments
Finances.cor.matrix <- rcorr(as.matrix(finances))
kable(Finances.cor.matrix$r, caption = "Relationships between Income and Payment Methods")
```



## Relationships between Finances and PECTAC Expectations

The main question here is -- Is there a relationship between how paretns are paying and their expectations? We will look at a few aspects to analyze this question.  
Is there a relationship between parent's TaxIncome2013 with their PECTAC expectations?  
Is there a relationship betwen parent's use of family assets to pay for college with their PECTAC expectations?  
Is there a relationship between parent's use of Parent Borrowing to pay for college with their PECTAC expectations?  
Is there a relationship between parent's use of Current Parent Income to pay for college with their PECTAC expectations?  

```{r Row means}
# Get row means for each scale
# Essentially, each variable is the mean score for each parent of the questions across each entire scale.
# e.g. parent #1 had a mean score of 1.00, parent #2 had a mean score of 1.07, etc.
Techrowmean <- rowMeans(Tech, na.rm = TRUE)
ATLrowmean <- rowMeans(ATL, na.rm = TRUE)
CFrowmean <- rowMeans(CF, na.rm = TRUE)
CUCrowmean <- rowMeans(CUC, na.rm = TRUE)
BPProwmean <- rowMeans(BPP, na.rm = TRUE)
OCLrowmean <- rowMeans(OCL, na.rm = TRUE)

# Matrix that contains each parent's Tax Income with their (mean) score for each scale
DF1 <- as.data.frame(cbind(TaxIncome2013, FamAssets, PBorrow, CPI, Techrowmean, ATLrowmean, OCLrowmean, CFrowmean, CUCrowmean, BPProwmean))
#DF1 <- filter(DF1, complete.cases(DF1) == TRUE)
kable(rcorr(as.matrix(DF1))$r)
```


### 1. Is there a relationship between parent's TaxIncome2013 with their PECTAC expectations?

```{r Lin Reg to determine if relationship with Tax Income, collapse=TRUE}
# Lin reg for TECH ~ Tax Income
lm1 <- lm(Techrowmean ~ FamilyIncome2013BTax, data = DF1)
summary(lm1)  
  
# Lin reg for ATL ~ Tax Income
lm2 <- lm(ATLrowmean ~ FamilyIncome2013BTax, data = DF1)
summary(lm2)  
  
# Lin reg for CF ~ Tax Income
lm3 <- lm(CFrowmean ~ FamilyIncome2013BTax, data = DF1)
summary(lm3)  
  
# Lin reg for CUC ~ Tax Income
lm4 <- lm(CUCrowmean ~ FamilyIncome2013BTax, data = DF1)
summary(lm4)  
  
# Lin reg for BPP ~ Tax Income
lm5 <- lm(BPProwmean ~ FamilyIncome2013BTax, data = DF1)
summary(lm5)  
  
# Lin reg for OCL ~ Tax Income
lm6 <- lm(OCLrowmean ~ FamilyIncome2013BTax, data = DF1)
summary(lm6)
```

Answer:  Linear regressions computed above show there is no relationship between parent's TaxIncome2013 and their PECTAC expectations in categories 1, 2, 4-6.  There is a slight relationship (p=0.0015) between TaxIncome2013 and A Caring Faculty.  
(Justin, do we want to elaborate on this?)  


### 2. Is there a relationship between parent's use of family assets to pay for college with their PECTAC expectations?

Answer:  Linear regressions showed there is no relationship between parent's use of family assets to pay for college and their PECTAC expectations in categories 1, 2, 4-6.  There is a slight relationship (p = 0.0018) between use of family assets to pay for college and A Caring Faculty.  
(do we want to elaborate on this?)  

### 3. Is there a relationship between parent's use of borrowing to pay for college with their PECTAC expectations? 

Answer:  Linear regressions show that there is a slight negative relationship (p = 0.0080) between parents borrowing to pay for their child’s college and how they viewed the importance of Tech Resources in support of learning.  There was no significant relationship between use of borrowing to pay for college with the other five PECTAC scales.  

### 4. Is there a relationship between parent's use of current income to pay for college with their PECTAC expectations?

Answer:  There was no relationship found between parent’s use of current income to pay for their child’s college with any of their PECTAC expectations.








*****
Statistical analysis done by Billy Jackson from November 2016 - February 2017  
Updated for public viewing on July 6, 2017  
[Email](action781@gmail.com)  |  [Homepage](https://sites.google.com/northshore.edu/billy-jackson/home)  |  [Github](www.github.com/action781)








